An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-14 VLDB2026/main.tex
Revert "Merge branch 'main' of https://github.com/zhujx001/Hybrid-ANNS"
This reverts commit 8bb04b9d801713304c88506f7431ea6357882dc1, reversing
changes made to 9027b0d595526968d6730e2594e92382d81226ff.
add CAPS exp 2

	\textit{Effect of Multi-Attribute Building on Algorithm Performance (M vs. S).}
	As shown in Figure \ref{fig:exp_2_1}, Puck demonstrates nearly no performance degradation. In contrast, the performance of StitchedVamana, FilteredVamana, NHQ, and UNG drop significantly, with the following reasons: 1) FilteredVamana increases the complexity introduced by retaining attribute during index construction. 2) The complexity of StitchedVamana increases because data points may duplicate across multiple subgraphs. 3) The fusion distance of NHQ exhibits sensitivity to the number of attributes, which degrades its effectiveness. 4) The reason why UNG has poor performance is that each base vector has 8 attributes, but only one query attribute, which results in a large number of entry points that need to be traversed. It is difficult for a graph with multiple entries to have good connectivity, degenerating into a situation closer to inverted retrieval, and the effect may be greatly impaired.

	\textit{Performance of Algorithms under Multi-Attribute Building (M vs. M).}  
	As shown in Figur \ref{fig:exp_2_1}, Puck achieves the best query performance, surpassing other algorithms by an order of magnitude. It filters out irrelevant results during retrieval rather than searching for more candidates. FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, hurting single-attribute query efficiency. This leads to excessive irrelevant node traversal, making it slower than other methods.

>>>>

	\textit{Effect of Multi-Attribute Building on Algorithm Performance (M vs. S).}
	As shown in Figure \ref{fig:exp_2_1}, Puck and CAPS demonstrate nearly no performance degradation. In contrast, the performance of FilteredVamana,StitchedVamana, NHQ, and UNG drop significantly, with the following reasons: 1) FilteredVamana increases the complexity introduced by retaining attribute during index construction. 2) The complexity of StitchedVamana increases because data points may duplicate across multiple subgraphs. 3) The fusion distance of NHQ exhibits sensitivity to the number of attributes, which degrades its effectiveness. 4) The reason why UNG has poor performance is that each base vector has 8 attributes, but only one query attribute, which results in a large number of entry points that need to be traversed. It is difficult for a graph with multiple entries to have good connectivity, degenerating into a situation closer to inverted retrieval, and the effect may be greatly impaired.

	\textit{Performance of Algorithms under Multi-Attribute Building (M vs. M).}  
	As shown in Figur \ref{fig:exp_2_1}, CAPS has the best QPS performance, while Puck has better recall accuracy. CAPS first partitions by clustering, and then builds AFT under each partition. For CAPS, whether it is built with multiple attributes or a single attribute, the number of points required to be retrieved will not change after AFT filtering during search, so the performance is not greatly affected. Puck filters out irrelevant results during retrieval rather than searching for more candidates. FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, hurting single-attribute query efficiency. This leads to excessive irrelevant node traversal, making it slower than other methods.
